Verifying Demonstrations

### 2018-11-01 paper/DB-anon-cred.tex
minor changes to section V-C + tinkering with references.bib re:compilation issues

In the original \ac{DB} paper by \citet{DistanceBounding}, one of the 
distance-bounding protocols is based on the Schnorr identification 
scheme~\cite{Schnorr}.
However, this \ac{DB} Schnorr protocol was shown to be prone to distance hijacking~\cite{DistanceHijacking, TamarinDB}, in addition to not being secure against terrorist fraud.
We now propose another way to turn the Schnorr protocol into a
public-key \ac{DB} protocol which is secure against \ac{DBMF},
\ac{DBDF}, \ac{DBDH} and \ac{DBTF}.
It is important in our setting that the protocol is a public-key protocol, this 
property implies protection against an impersonating verifiers.

@@

We wanted to formally verify the protocol security properties. We used the Tamarin prover~\cite{meier2013tamarin}. Tamarin does not include timestamp and location data in its model, but thanks to the work by Mauw \emph{et al.}~\cite{TamarinDB}, we know that all the common properties mentioned in the previous subsection can be equivalently characterized with a causality-based definition relying only on the order of messages.

The whole Tamarin code we wrote is provided in Appendix \ref{apdx:tamarin-spec}. It contains a specification of the distance-bounding protocol described previously, a definition of the soundness and correctness properties that ensure the protocol actually produces the expected result, and a definition of the security properties we want to ensure.

Tamarin auto-prover validated the soundness and correctness properties (in negligible computation time) but does not terminate when trying to prove the security properties, that is to say, no trace violating the security properties is found, but the prover cannot conclusively validate that the properties are true. We are currently investigating with Tamarin interactive mode to hopefully validate the security properties as well.

\sonja{\subsection{Formal Verification} 
 verification with tamarin: there is no BC Schnorr in Tamarin,  [10]
assumed equivalence with Fiat-Shamir model. Not straightforward to
implement Schnorr in Tamarin due to a lack of expressiveness for
arithmetic needed to complement Diffie-Hellman. If not done now, left
for future work. }

>>>>

In the original \ac{DB} paper by \citet{DistanceBounding}, one of the distance-bounding protocol is based on the Schnorr identification scheme~\cite{Schnorr}. 
However, this \ac{DB} Schnorr protocol was shown to be prone to distance hijacking~\cite{DistanceHijacking, TamarinDB}, in addition to not being secure against terrorist fraud.
We now propose another way to turn the Schnorr protocol into a
public-key \ac{DB} protocol which is secure against \ac{DBMF},
\ac{DBDF}, \ac{DBDH} and \ac{DBTF}. a
It is important in our setting that the protocol is a public-key protocol, this 
property implies protection against an impersonating verifiers.

@@

We wanted to formally verify the protocol security properties. We used the Tamarin prover ~\cite{meier2013tamarin}. Tamarin does not include timestamp and location data in its model, but thanks to the work by Mauw \emph{et al.}~\cite{TamarinDB}, we know that all the common properties mentioned in the previous subsection can be equivalently characterized with a causality-based definition relying only on the order of messages.

The whole Tamarin code we wrote is provided in Appendix \ref{apdx:tamarin-spec}, with a short discussion of the modelization choices we made. It contains a specification of the distance-bounding protocol described previously, a definition of the soundness and correctness properties that ensure the protocol actually produces the expected result, and a definition of the security properties we want to ensure.

The Tamarin auto-prover validated the soundness and correctness properties (in negligible computation time) but does not terminate when trying to prove the security properties, that is to say, no trace violating the security properties is found, but the prover cannot conclusively validate that the properties are true. We are currently investigating with Tamarin interactive mode to hopefully validate the security properties as well.
